Appendix0\_10

### 2018-08-17 paper/Appendices/AppendixC.tex
appendix C figlevel 1 CW4

\chapter{Example of a food diary for one day} % Main appendix title

\label{AppendixC} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}
%\begin{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary1.png}
\decoRule
\caption[One day food diary example 6 am to 2 pm]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 6 am to 2 pm.}
\label{fig:diary1}
\end{figure}
%\end{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary2.png}
\decoRule
\caption[One day food diary example 2 pm to 6 am]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, from 2 pm to 6 am.}
\label{fig:diary2}
\end{figure}
%\end{verbatim}

\begin{figure}[H]
%\vspace*{13cm}
\centering
\includegraphics{Figures/Diary3.png}
\decoRule
\caption[Food diary example of home made food recipes]{NATIONAL DIET AND NUTRITION SURVEY -- Food and Drink Diary Example, home made food recipes.}
\label{fig:diary3}
\end{figure}

>>>>

\chapter{Other Solutions for MLCA} % Main appendix title

\section{2 classes in day level}

\label{AppendixC} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics{Figures/CW2level1.png}
	\decoRule
	\caption[2 Classes solution in Day level]{2 Classes solution in Day level.}
	\label{fig:diary1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB2.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 2).]{Multilevel Latent Class Solution, 2 classes in day level, 2 classes in individual level.}
	\label{fig:diary1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB3.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 3).]{Multilevel Latent Class Solution, 2 classes in day level, 3 classes in individual level.}
	\label{fig:diary1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB4.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 4).]{Multilevel Latent Class Solution, 2 classes in day level, 4 classes in individual level.}
	\label{fig:diary1}
\end{figure}

\section{3 classes in day level, 4 classes in individual level}\vspace{-0.3cm}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW3CB4.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (3 $\times$ 4).]{Multilevel Latent Class Solution, 3 classes in day level, 4 classes in individual level.}
	\label{fig:diary1}
\end{figure}

\section{4 classes in day level}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=15cm]{Figures/CW4level1.png}
	\decoRule
	\caption[2 Classes Solution in Day level]{4 Classes Solution in Day level.}
	\label{fig:diary1}
\end{figure}
